Dynamics of Laterally Propagating Flames in X-ray Bursts. I. Burning Front Structure

### 2020-02-11 xrb/submit/paper.tex
Added additional paragraph on Yuri's papers to intro

>>>>

However, the computational expense of the problem necessitated several approximations
to make this set of simulations \citep{cavecchi:2013, art-2015-cavecchi-etal, art-2016-cavecchi-etal, Cavecchi2019}
tractable. The first was the assumption of vertical hydrostatic equilibrium, which allowed them
to filter out vertically propagating sound waves that would otherwise have limited the
timestep. Although this enabled them to reach the simulation times (on the order of seconds) needed
to capture the rise of the burst, they could not model vortical fluid motions driven by effects such
as turbulence and convection. These can facilitate mixing and help to accelerate the propagation of
the flame front. They also include only the triple-$\alpha$ process in their implementation of
nuclear burning, neglecting the other reaction chains at play in a pure He burst. Our simulations
relax the assumption of vertical hydrostatic equilibrium and implement a more complete set
of nuclear reactions.
